%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Manoj Kalaivanan}
\address{13031 123rd Ln NE \#D203 \linebreak Kirkland WA 98034}
\contacts{+1 (206) 229-4075 \linebreak manoj.ceg@gmail.com}

\begin{document}
	% Print the header
	\makeheader
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Full Stack Software Engineer}{Groupon Inc, Seattle}{Jan, 2016 -- Present}
			\item \strong{Things To Do Team} -- JavaScript; Backbone; NodeJS; Ruby on Rails;  MySQL;--
			\begin{itemize}
			 	\item Designed and implemented Things To Do free event listings.
				\item Modified the GrouponLive inventory service to reduce the latency and increase the throughput of an endpoint with requests in the order of 100K per second.
				\item Designed and implemented context specific filters to enable better discovery of deals in Groupon's Local category.
				\item Lead the holiday readiness process to ensure applications were ready for high peak traffic season.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{Groupon, Chennai, India}{Feb, 2014 -- Jan, 2016}
			\item \strong{Goods Team} -- Java; Play(Java); PostgreSQL; --
			\begin{itemize}
				\item  Lead the design and implementation of Inbound scheduling service which enables the goods merchants to schedule pickups with the Groupon's preferred shipment carriers and reduce the delivery time to customers.
				\item Implemented email notification service to notify the customers in 7 APAC countries about the progress of their shipment.
				\item Maintained Post order processor, an address cleansing service for orders in the APAC countries. It handled around 10K orders everyday.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Senior Software Engineer}{Samsung Research Institute, Bangalore, India}{Dec, 2010 -- Jan, 2014}

			\item  \strong{Mobile Browser Team} -- C/C++; Java; Trace32 Hardware debugging;--
			\begin{itemize}
				\item Developed and maintained browser and downloader applications for feature phones operating on Samsung's proprietary handset platform.
				\item Optimized a browser engine which is based on Webkit by addressing the memory leaks and made it compatible on feature phones with limited RAM.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Chennai, India}{College of Engineering, Guindy}{August, 2006 --  May, 2010}
		
			\begin{itemize}
			\end{itemize}
			\begin{itemize}
				\item Bachelor of Engineering in Computer Science. {      }{      }{      }{      } {      }{      }{      }{      } {      }{      }{      }{      } {      }{      }{      }{      } {      }{      }{      }{      } {      }{      }{      }{      } {      }{      }{      }{      } {      }{      }{      }{      }  {      }{      }{      }{      } {      }{      }{      }{      } {      }{      }{      }{      } {      }CGPA: 8.26 / 10
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
		\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Resource optimization in data center} (2010) -- Worked along with IBM and developed a Virtual Machines Monitor in host virtual machine(VM) running in the Xen hypervisor. This will increase or decrease the number of guest VMs based on the CPU usage of them.
				\item \textbf{DDOS attack simulation and prevention techniques} (2009) -- Developed a DDOS attack simulation tool which spoofs the IP address in the requests and initiate Smurf attack or SYN flooding on any given destination. This was demonstrated in the 10th Workshop of
Smart and Secure Environment conducted by National Technical Research Organization(NTRO), New Delhi.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item C/C++; Ruby; JavaScript; SQL; Java;
				\item Ruby on Rails; MySQL; PostgreSQL; NodeJS; Play(Java);
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
